---
title       : Slidify Test
author      : Paul Maley
job         : Aspiring Data Scientist
framework   : io2012          # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js    # {highlight.js, prettify, highlight}
hitheme     : tomorrow        # 
widgets     : []              # {mathjax, quiz, bootstrap}
mode        : selfcontained   # {standalone, draft}
---

## The Mouse-itis model
A light-hearted model for experimenting with some features of R and some data-presentation packages; in particular:

 - Shiny - for a web-based presentation of the model
 - Slidify - for a brief presentation of the application

The model is based on two random variables: 
 - A binary random variable determining whether an individual is afflicted or not
 - A normal random variable generated with a mean that is higher for afflicted individuals 

---

## Probability model

The graph shows the probability of having a given level of frustration for sufferers and non-sufferers
for typical values of the affliction probability and the mean frustration levels.

```{r, echo=FALSE, results='hide', fig.height=6}
  library(ggplot2)
  library(reshape2)

  fl <- seq(0,100)    # frustration levels
  sd_frust <- 10.0   # std deviation of frustration (equal for both populations)
  sufferer_mean_frust <- 70
  non_sufferer_mean_frust <- 30
  red_black_scale <- c("red", "black")
  pct_occurence <- 0.1

  df <- data.frame(level=fl, 
                   suffurers =  pct_occurence * dnorm((fl-sufferer_mean_frust)/sd_frust),
                   non_suffurers = (1 - pct_occurence) * dnorm((fl-non_sufferer_mean_frust)/sd_frust)
                  )

  df <- melt(df, c("level"),  variable.name=c("SubPopulation"), value.name=c("Occurence"))

  ggplot(df) + geom_area(aes(x=level, y=Occurence, group=SubPopulation, 
                            fill=SubPopulation), alpha=0.5) +
               xlab("Frustration level") + 
               theme(legend.position="bottom") + 
               scale_fill_manual(values=red_black_scale)
```

---
 
## Predicting the condition
Two logistic regressions are performed on the data
 - The first assumes that only the level of frustration is known.
 ```{r,eval=FALSE}
 mdl <- formula(Afflicted ~ FrustrationLevel)
 glm(mdl, family=binomial(logit), data=sample_data)
 ```
 - The second assumes the existence of a test; this test has probabilities to result
   in false positive and false negative results.
 ```{r,eval=FALSE}
 mdl <- formula(Afflicted ~ FrustrationLevel + TestResult)
 glm(mdl, family=binomial(logit), data=sample_data)
 ```
 - Since this is only for illustration, no cross-validation or test data sets are used.


---

## Diagnosis

- The result of the logistic regression is a model which maps the frustration level and test result to a probability of affliction.

- By varying a probability threshold, the accuracy, precision and recall of the diagnosis can be varied.

- The aim of this application is to illustrate how the various factors (symptoms of affliction, a priori occurence of the condition, diagnosis threshold and test fidelity) interplay.



